---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# bs2site

**Don't expect this package to work outside of our specific application**

The bs2site package is used to build our teaching websites ([biostat2.uni.lu](https://biostat2.uni.lu) or [rworkshop.uni.lu](https://rworkshop.uni.lu)). These websites combine different Rmarkdown formats in order to include practicals and lectures.

Our websites are built on gitlab using continuous integration (CI). `bs2site` helps to:

- identify which packages are used in active documents (not starting with `_`)
    + tries to install missing packages from cran.
    + installs packages hosted on github or bioconductor which were defined in a `package.yml` file.
- add a branding logo in the navbar header.
- save and load objects saved as `rds` files in a standardised location (_i.e._ used as a cache synced with git LFS).
- provide an Rstudio addin to interact with the gitlab instance
    + configure the access to gitlab and store the private token in the system credential store (using the `keyring` package)
    + deploy the website (production: manual action)
    + build the website without using the CI cache (rebuild)

## Installation

You can install bs2site from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("koncina/bs2site")
```

## Folder structure

The folder structure of the website source directory is the following:

```
├── lectures
│   ├── img
│   ├── lecture_01.Rmd
│   └── ...
├── practicals
│   ├── img
│   ├── TD_01.Rmd
│   └── ...
├── site
│   ├── img
│   ├── index.Rmd
│   └── ...
└── ...
```

### Lectures

Each lecture should be placed in the `lectures` folder and named as `lecture_xx.Rmd` where `xx` is a zero padded number. The format used to render the lectures is [iosp](https://github.com/koncina/iosp).

### Practicals

Each practical should be placed in the `practicals` folder and named as `TD_xx.Rmd` where `xx` is a zero padded number. The format used to render practicals is [unilur](https://github.com/koncina/unilur).

### Main site pages

All remaining pages to setup the website are placed in the `site` folder.

## Generating the site

Configure the project to use the `Makefile` which will render the website in the `docs` output folder.

## Helper functions

The `bs2site` package contains some helper functions used to render the site. Have a look at the references on `http://koncina.github.io/bs2site/`.

