---
title: "Box colours"
author: "Eric Koncina"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    css: box.css
vignette: >
  %\VignetteIndexEntry{Box colours}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(dplyr)
library(purrr)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<style>

```{r, results = 'asis', echo = FALSE}
cat(bs2site:::create_box_css(path = NULL))
```

</style>

In order to use a standardised set of box colours, we defined the following box types:

```{r, echo = FALSE}
bs2site:::get_box_colours() %>%
  select(name, description) %>%
  knitr::kable()
```

## Colour preview

### Default boxes

To generate the above described box colours, just add the class: `### Header {.box-4 .intro}`

```{r, echo = FALSE}
draw_box <- function(colour, outline = FALSE) {
  htmltools::h3("Header") %>% htmltools::div(class = glue::glue("box {colour} {if_else(outline, 'outline', '')}"),
                                             "Some text using", htmltools::br(),
                                             htmltools::code(paste0(colour, if_else(outline, ' outline', '')))
                                             )
}
```

```{r, echo = FALSE, results = "asis"}
colours <- pull(bs2site:::get_box_colours(), name)

purrr::map(colours, draw_box) %>%
  htmltools::div(class = "box-container") %>%
  htmltools::doRenderTags()
```

### Outline boxes

Outline boxes exhibit a white background and only use the header/border colour. Just add the `.outline` class to your box (_e.g._ `### Header {.box-4 .intro .outline}`)

```{r, echo = FALSE, results = "asis"}
purrr::map(colours, draw_box, outline = TRUE) %>%
  htmltools::div(class = "box-container") %>%
  htmltools::doRenderTags()
```

## Include or update the colours in your site

The colours are defined in a `css` file. I you're using a site configured as expected by the `bs2site` package, simply run the `use_box_colours()` function to create (or update) the file. A link to the css file is automatically added to the `lectures/_output.yml` file.